---
author: "Gavin Fay"
date: "6/4/2020"
output: html_document
---

Read in TXT file for JBA & HB.    
Contains the example used to build the code, then I turn this into a function `get_id_data()` which takes a filename as input.  
Finally, then show an application to run this over a list of filenames (say for all the .TXT files in a given directory), and combine them into a single data frame.  

## load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(janitor)
```

## read in data file example

```{r read-data}
file <- "data/05262020_mckenzie_cartney.TXT"
raw_data <- readLines("data/05262020_mckenzie_cartney.TXT", warn = TRUE)
raw_data <- gsub("[^0-9A-Za-z///' ]", "", raw_data)
# #raw_data
# raw_data <- read.table("data/05262020_mckenzie_cartney.TXT", col.names = 1:100, fill = TRUE, sep = ",", stringsAsFactors = FALSE)
start <- grep("ID  Sensor and GPS Positions", raw_data)
stop <- grep("Manually Triggered Coded Records", raw_data)-2

id_data <- read_table(file, skip = start, n_max = (stop-start-2))
# tail(id_data)
id_data <- janitor::clean_names(id_data) %>% 
  separate(date_time, sep = 9, into = c("date", "time")) %>% 
  mutate(date = lubridate::mdy(date),
         time = lubridate::hms(time))
    #year = lubridate::year(date),
     #    month = lubridate::month(date),
      #   day = lubridate::day(date)) #,
         #time = lubridate::time(time))
id_data
```


## create generic function to run for a given filename  

```{r read-func}

get_id_data <- function(file) {
  #function reads in id sensor data from a single file
  #
  #first find where the data is
  raw_data <- readLines(file, warn = TRUE)
  raw_data <- gsub("[^0-9A-Za-z///' ]", "", raw_data)
  start <- grep("ID  Sensor and GPS Positions", raw_data)
  stop <- grep("Manually Triggered Coded Records", raw_data)-2

  #now read in the data table
  id_data <- readr::read_table(file, skip = start, n_max = (stop-start-2))
  #do some minimal cleaning to get meaningful/useable columns, headers, etc.
  id_data <- janitor::clean_names(id_data) %>%   #formats headers nicely
    separate(date_time, sep = 9, into = c("date", "time")) %>%  #splits the date from the time
    mutate(date = lubridate::mdy(date), #turns date string into a date object
           time = lubridate::hms(time), #turns time string into a time object
           filename = rep(file,nrow(id_data))) #create a column with the name of the file
  return(id_data)
}
#example run of function
file <- "data/05262020_mckenzie_cartney.TXT"
get_id_data(file)

```


## Application over many files
```{r}
#find all the files with the right extension
files <- dir(path = "data/",  # I put your 
             pattern = "*.TXT",
             full.names = TRUE)
#files object is now a vector of filenames

#read all the files in and combine everything into a single data frame
id_sensor_data <- map_dfr(files, get_id_data) 
   # map runs 'get_id_data' for each of the things in 'files'.  
   # The '_dfr' puts the output into a data frame, combined via rows. 
#id_sensor_data
```



