---
title: "noaa-sentiments"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(sentimentr)
library(jsonlite)
```
## Look at sentiment of NOAA rulese since 2001.
Goal is to see if 2020 rules post-COVID are more positive than pre-COVID.

## Get data from the federal register
Pull from the federal register
Currently a hard-coded search for NOAA from 2001-01-01 to present, type = rules

```{r pulldata}
#temp$count
#[1] 600137

# xx <- fromJSON("https://www.federalregister.gov/api/v1/documents?conditions%5Bagencies%5D%5B%3Dnational-oceanic-and-atmospheric-administration%5D=&conditions%5Bpublication_date%5D%5Bgte%5D%5B%3D2001-01-01%5D=&format=json&page=0",flatten = TRUE)

pull_regs <- function(x) {
page <- paste0("https://www.federalregister.gov/api/v1/documents?conditions%5Bagencies%5D%5B%5D=national-oceanic-and-atmospheric-administration&conditions%5Bpublication_date%5D%5Bgte%5D=01%2F01%2F2001&conditions%5Bpublication_date%5D%5Blte%5D=05%2F28%2F2020&conditions%5Btype%5D%5B%5D=RULE&format=json&page=",x,"&per_page=1000")
 xx <- fromJSON(page, flatten = TRUE)$results
 return(xx)
}
#get number of pages in search
page <- paste0("https://www.federalregister.gov/api/v1/documents?conditions%5Bagencies%5D%5B%5D=national-oceanic-and-atmospheric-administration&conditions%5Bpublication_date%5D%5Bgte%5D=01%2F01%2F2001&conditions%5Bpublication_date%5D%5Blte%5D=05%2F28%2F2020&conditions%5Btype%5D%5B%5D=RULE&format=json&page=0&per_page=1000")
fpage <- fromJSON(page, flatten = TRUE)
npage <- fpage$total_pages

plan(multiprocess)
system.time(regs <- future_map_dfr(1:npage,pull_regs))
range(regs$publication_date)
regs <- tibble(regs)
```

## Look at the sentiment of the abstracts of these rules

Using `sentimentr` package. to find average sentiment of sentences in the abstracts.    

```{r sentiment}
# rules by NOAA
regs_part <- regs %>%
   unnest(cols = "agencies") %>% 
   filter(name == "National Oceanic and Atmospheric Administration",
          type == "Rule") %>%
  I()
regs_part

# sentiments of sentences of the abstract and then average over abstracts
regs_sentiment <- regs_part %>% 
  select(publication_date, title, type, abstract, document_number) %>% 
  rowid_to_column() %>% 
  mutate(sentences = map(abstract,get_sentences),
         sentiment = map(sentences,sentiment_by)) %>% 
  unnest(cols = sentiment) %>% 
  I()


# make publication date more easy to work with
regs_summary <- regs_sentiment %>% 
  select(publication_date, ave_sentiment) %>% 
  mutate(date = lubridate::date(publication_date),
         year = lubridate::year(publication_date)) %>% 
  I()

```

## viz

summarize by year

```{r plot-sentiment}


regs_summary %>%
  ggplot() +
  #aes(y = ave_sentiment, x = factor(year)) +
  aes(y = ave_sentiment, x = date) +
  #geom_boxplot() +
  geom_jitter(alpha = 0.5) +
  geom_smooth() +
  NULL

regs_summary %>%
  ggplot() +
  aes(y = ave_sentiment, x = factor(year)) +
  geom_boxplot() +
  theme_minimal() +
  labs(x = "year",
       y = "average sentiment",
       title = "NOAA rules in federal register more positive in 2020",
       subtitle = "average sentiment of abstracts of NOAA Rules",
       caption = "\n@gavin_fay\ndata from https://federalregister.gov") +
  #geom_jitter(alpha = 0.5) +
  #geom_smooth() +
  NULL

ggsave("noaa-sentiment-yr.png",width = 8, height = 4.5)
```

A qnd linear model suggests positive effect of 2020 is statistically clear.

```{r}
regs_lm <- regs_summary %>% 
  mutate(twenty = ifelse(year==2020, 1, 0)) %>% 
  lm(ave_sentiment~twenty,data=.) %>% 
  tidy() %>% #augment()
  I()
regs_lm
```

